`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-17 inst/manuscript/manuscript.rmd
Minor clarification that 'Table S2' is NOT in the current manuscript but in Ploier et al. (2016);

The resulting values for the fit constant correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_dimerization_2016 (Table S2), where $\alpha
\times 10^4 \approx 16$ was reported for mutant and $\alpha \times 10^4 \approx
7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
in @ploier_dimerization_2016 that the mutant rhodopsins investigated are
reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.

>>>>

The resulting values for the fit constant correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_dimerization_2016 (Table S2 therein), where
$\alpha \times 10^4 \approx 16$ was reported for mutant and 
$\alpha \times 10^4 \approx 7$ for wild type rhodopsin. Based on the manual
analysis of the data we conclude in @ploier_dimerization_2016 that the mutant
rhodopsins investigated are reconstituted into proteoliposomes in monomeric
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.
